Air cargo load and route planning in pickup and delivery operations

### 2024-01-31 latex/eswa.tex
Article update

>>>>

Inefficient air transport plans can lead to unnecessary costs, extra routes, longer distances, and incorrect destinations. Unbalanced cargo increases fuel consumption due to altered aircraft pitch angles.

A study by \cite[p. 22]{gwh2007} highlights the risk of weight- and balance-related accidents on cargo flights compared to passenger flights. So, balancing cargo is crucial for safe aerial transportation, as an improperly positioned centre of gravity can result in dangerous take-off and landing conditions and stall recovery issues.

Another important issue is managing fuel consumption. To get an idea of the influence of CG displacement on fuel consumption, \cite[p. 140]{MongeauBes2003} report that {\it "a displacement of the CG of less than 75 cm in a long-range aircraft yields, over a 10,000 km flight, a saving of 4,000 kg of fuel"}. This reinforces the importance of balancing cargo.

Despite technological advancements, many airlines still rely on manual aircraft loading and balancing, using simple computer-aided tools for CG computation and constraint testing. Loadmasters often create load plans manually, which is time-consuming and can lead to flight delays.

As to the right delivery, an organisation's purchasing department may acquire supplies in the main capitals of the country and abroad to meet the company's needs, and it wants these materials to be delivered to the requesting organisations within the stipulated deadlines.

A rational decision-making process is crucial to avoid creating inefficient or unsafe transport plans, considering the high costs of fuel, maintenance, operation, outsourcing expenses, potential operational impairments, and safety risks due to unbalanced cargo.

Solving the ACLPP+RPDP is vital for optimising strategic scores of what must be transported, saving time and effort in loading, ensuring safety and balance, ensuring correct pickups and deliveries, and finding the best routes considering fuel use due to potential cargo imbalance.
